---
title: "Practical Machine Learning Project"
author: "chen"
date: "8/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in the dataset
```{r}
library(caret)
library(ggplot2)
setwd("~/Coursera class/C8")
training <- read.csv("./data/pml-training.csv", header=TRUE)
dim(training)
testing <- read.csv("./data/pml-testing.csv", header=TRUE)
dim(testing)
```
## Take a look at content of the training data
```{r}
table(training$classe)
str(training)
```
## Data Prep
Split the training further into two parts -training and test.  At the same time exclude all the columns that are mostly NA or irrelevant
```{r}
inTrain <- createDataPartition(y=training$classe, p=0.7, list=FALSE)
train <- training[inTrain, c(6:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160 )]
test <- training[-inTrain, c(6:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160 )]
dim(train)
dim(test)
```

## Prep y variable
Since we will use randomForest, we need to set y variable to factor
```{r}
train$classe <- factor(train$classe)
test$classe <- factor(test$classe)
```

## Model building
Use randomForest with 500 trees; Print out variable importance

```{r}
library(randomForest)
set.seed(4543)
modFit.rf <- randomForest(classe ~ ., data=train, ntree=500, keep.forest=TRUE, importance=TRUE)
modFit.rf
varImpPlot(modFit.rf)
```
## Apply the model to test data
```{r}
pred3 <- predict(modFit.rf, newdata=test)
```

## Model Evaluation
Look at how accurate the predition is:
```{r}
table(pred3, test$classe)
confusionMatrix(pred3, test$classe)
```

## Show Tree
Try to plot a tree using the 3 most important variables

```{r}
library(partykit)
train$classe <- factor(train$classe)
y <- ctree(classe ~ num_window + roll_belt + yaw_belt, data = train)
plot(y, gp = gpar(fontsize = 6),  
     inner_panel=node_inner,
     ip_args=list(
       abbreviate = TRUE, 
       id = FALSE)
)
```


## Finally, predict the actual test cases in quiz
```{r}
pred4 <- predict(modFit.rf, newdata=testing)
pred4
```
# got it right 100%
